BioTime

### 2019-05-16 biotime.Rmd
Clean up checking alt matches back to itis, preserve original input column to join back to data.

#match all the un-ID'd names to other providers, check if synonyms given by those providers match known ITIS species 
alt_names <- map_df(providers, function(name) synonyms(unmatched, name)) %>%
  drop_na(acceptedNameUsageID)

syn_res <- bind_rows(by_name(na.omit(unique(alt_names$synonym)),"itis"),
                     by_name(na.omit(unique(alt_names$acceptedNameUsage)),"itis")) %>%
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  drop_na(id) %>% 
  distinct() %>%
  inner_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input)

>>>>

#match all the un-ID'd names to other providers, check if synonyms given by those providers match known ITIS species 
alt_names <- map_df(providers, function(name) synonyms(unmatched, name)) %>%
  drop_na(acceptedNameUsageID) %>%
  #new matches can be in either the synonym or acceptedNameUsage column, so let's combine them
  gather(type, altProviderName, synonym, acceptedNameUsage) %>%
  select(altProviderName, input) %>% 
  distinct()

#match accepted names from 
syn_res <- by_name(na.omit(unique(alt_names$altProviderName)),"itis") %>%
                       rename(altProviderName = input) %>%
                       left_join(alt_names) %>%
  select(id = acceptedNameUsageID, input, scientificName) %>% 
  drop_na(id) %>% 
  distinct() %>%
  left_join(data %>% select(-species, -genus), by = c("input" = "genus_species"), na_matches =  "never") %>%
  rename(matchingName = input)
